Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Multi-Notch Searches

### 2017-10-17 paper.tex
jdfkj

In the original G-PTM-D manuscript, an open mass search (+/- 200-500Da) was used to create a histogram of mass difference peaks, from which a number of PTMs could be inferred.
A perl script was used to mine those mass differences to modify a proteomics database with potential PTMs.
This database was used for a final search and a number of PTMs were identified.
There were several limitations to that work.
One, the open mass search was really slow.
Two, uncalibrated data made it hard to discern closely spaced modifications.
Three, certain mass differences with high FDRs were incorrectly allowed.
Four, missed monoisotopic peaks and co-isolated peaks were not handled.
Five, separate programs were required (both Morpheus and a perl script).
MetaMorpheus resolves all of these issues and more.
Below we will show how each individual enhancement to G-PTM-D improved performance over the original work and then we will show at the end, the combined effect of all enhancements.

>>>>

In the original G-PTM-D manuscript, an open mass search ($\pm 200-500 $ Da) was used to create a histogram of mass difference peaks, from which a number of PTMs could be inferred.
A Perl script was used to mine those mass differences to modify a proteomics database with potential PTMs.
This database was used for a final search and a number of PTMs were identified.
There were several limitations to that work.
One, the open mass search was really slow.
Two, uncalibrated data made it hard to discern closely spaced modifications.
Three, certain mass differences with high FDRs were incorrectly allowed.
Four, missed monoisotopic peaks and co-isolated peaks were not handled.
Five, separate programs were required (both Morpheus and a Perl script).
MetaMorpheus resolves all of these issues and more.
Below we will show how each individual enhancement to G-PTM-D improved performance over the original work and then we will show at the end, the combined effect of all enhancements.
